Choosing climate forcing for numerical simulations of the Cordilleran ice sheet

### 2013-02-12 sections/climate.tex
Added subsections in climate section
Added subsection 2.1 Observation data
Mostly typed in from paper draft with a few changes.

@@

>>>>

\subsection{Observation data}

WorldClim \citep{data:worldclim} is a high resolution climate dataset interpolated between from weather station data over global land areas. The interpolation uses 30\,arc\,s aggregated, hole-filled SRTM\needref data \todo{check WorldClim methods}, which provides a resolution much higher than attained by general circulation models.

However, the density of weather stations used by WorldClim in the Northern American Cordillera is highly inhomogeneous, and if good coverage exists in the southern parts of our modelling domain, several hundred kilometers can separate nearby stations in the north \citep{data:worldclim}.

A second drawback of the dataset in an ice sheet modelling view is the lack of data on marine surfaces, particularly on the Pacific continental shelf where glaciers have advanced during the last glacial cycle\needref.

% ----------------------------------------------------------------------

\subsection{Reanalysis data}

% ----------------------------------------------------------------------

\subsection{Cordillera climates}

@@

% ----------------------------------------------------------------------

\subsection{Preprocessing and lapse-rate corrections}
